%
% future.tex
%

I plan to use the user interviews from Chapter 4 and follow the process outlined by Alan Cooper and discussed in Chapter 3. The following subsections describe the proposed design creation process. After developing a design framework, I plan to implement the framework. I will try to further my knowledge of web frameworks during the implementation process. Once there is a functioning, deliverable product, I will develop an evaluation matrix and have the users re-evaluate each website from the initial interviews and my new product, producing scores and comparing my product with its competitors. Any problems found with my product during this evaluation, I will attempt to fix and then run usability testing again. In the end, the goal is to create an online planner that is more effective than the current options and entices students who use paper planners or no planner at all to switch over to my product.

\section{Modeling} 
In the next phase of development I will discover behavior and work flow patterns by analyzing the interviews. Subjects will be grouped together based on these patterns and synthesized into user models, or personas. Each persona will be designated a type, such as primary, secondary, and supplemental. These types will decided how influential each persona is on the design.

\section{Requirements Definition}
In Requirements Definition phase I will develop context scenarios, a "day in the life" of the persona using the product, and use these scenarios to analyze the functional and data requirements of users. I will also involve my own goals for the product and intertwine this information into a requirements definition, which balances user and technical requirements that the design will follow.

\section{Design Framework and Refinement}
In the Framework Definition phase I will produce a rough, high level sketch of the product views. The goal is to define the overall structure and user experience. The rough sketch will then be tested with scenarios, similar to context scenarios. These scenarios will test how well the persona can complete it's goals using the rough design. Then, I will increase the detail of the rough sketch and produce a detailed documentation of the design.